### 2021-06-22 docs/manuscript/manuscript.tex
Fix value of initial concentration of gene products
Correction made by Reviewer #2
State that morphogen dynamics is not considered

In our model the morphogen could interact with any of the three genes on the
GRN, but could not be affected by them. The morphogenetic field was defined by
an unidimensional array of 30 isogenic cells exposed to the morphogen
concentration gradient (Fig~\ref{fig:model}C). The initial concentration of
each gen product in all cells was set to 0.1 in all simulations.\\

@@

The morphogen concentration along the morphogenetic field is described by
Eq~\ref{ec:morph}.
\begin{equation}
 M = A_0 \cdot \exp(-c/h),
 \label{ec:morph}
\end{equation}
\noindent
were $A_0$ is the concentration of the morphogen in the position zero of the
morphogenetic field and was set to 1 in our experiments; $c$ is the cell index,
defined as the ratio between the \emph{n}-th cell from left to right and the
total number of cells, and $h$ is a decay parameter, whose value in our model
was set to 0.4.

>>>>

In our model the morphogen could interact with any of the three genes on the
GRN, but could not be affected by them. The morphogenetic field was defined by
an unidimensional array of 30 isogenic cells exposed to the morphogen
concentration gradient (Fig~\ref{fig:model}C). The initial concentration of
each gen product in all cells was set to 1 in all simulations.\\

@@

The morphogen concentration along the morphogenetic field is described by
Eq~\ref{ec:morph}.
\begin{equation}
 M = A_0 \cdot \exp(-c/h),
 \label{ec:morph}
\end{equation}
\noindent
were $A_0$ is the concentration of the morphogen in the position zero of the
morphogenetic field and was set to 1 in our experiments; $c$ is the cell index,
defined as the ratio between the \emph{n}-th cell from left to right and the
total number of cells, and $h$ is a decay parameter, whose value in our model
was set to 0.4. We do not consider here how the morphogen gradient can be
formed, i.e., we do not consider morphogen dynamics but we assume a static
gradient.
